Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-05-24 paper/ms.tex
minor updates in the paper

\author[~J.~E. Forero-Romero and J. Mejia]{
\parbox[t]{\textwidth}{\raggedright 
  Julian Mej\'ia$^{2}$ and
Jaime E. Forero-Romero$^{1}$}
\vspace*{6pt}\\
$^{1}$\\
$^{2}$ Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia 
}

@@

We calculate the mean angular correlation function (ACF) for all
models with $P>0.05$ using the match and random methods. These
correlation functions is calculated over the denseset subfield in all the
mock surveys corresponding to the SSA22 region. These results are
compared against the observations reported by Hayashino et al in 2004
over the same region, which were also performed on the densest field.

@@

@@

When we include the tightest constraints on the mock catalogs, we find
that there are 30 set of parameters of our model, out of the original
90000 initial models, that are consistent with the observational
constraints at redshift $3.1$: the distribution of the number density,
the inferred values for the average occupation fraction and the
angular correlation function.

>>>>

\author[~J.~E. Forero-Romero and J. Mejia]{
\parbox[t]{\textwidth}{\raggedright 
Jaime E. Forero-Romero$^{1}$ and
Julian Mej\'ia$^{2}$ 
}
\vspace*{6pt}\\
$^{1}$ Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia \\
$^{2}$ --}

@@

We calculate the mean angular correlation function (ACF) only for the
models that showed that all of the 15 mock surveys are consistent
at the $P>0.05$ level with observations. The ACF is computed only the
denseset subfield in all the 15 mock surveys corresponding to the
SSA22 region. These results are compared against the observations
reported by Hayashino et al in 2004 over the same region, which were
also performed on the densest field.

@@

We also present the results for the angular correlation function in
therms of the correlation lenght obtained by fitting the following
function

\begin{equation}
\xi(r) = \left(\frac{r}{r_{0}}\right)^{-\gamma}
\end{equation}

The results are shown in Figure in a $r_{0}-\gamma$ plane where the
average and standard deviation for each mock are shown in comparison
with the result derived from observations.

@@

When we include the tightest constraints on the mock catalogs, we find
that there are 30 set of parameters of our model, out of the original
90000 initial models, that are consistent with the observational
constraints at redshift $3.1$: the distribution of the number density,
the inferred values for the average occupation fraction. The
consistency with the angular correlation, in terms of the $\chi^2$
statistics did not help to discard any additional models with a
significant degree of confidence.
